On exponential sums arising from the classical doubling method

### 2025-03-20 paper.tex
Explaining the notation a bit

% Finite field macros
\newcommand{\FieldNorm}[2]{\mathrm{N}_{#1:#2}}
\newcommand{\aFieldNorm}{\mathrm{N}}
\newcommand{\finiteField}{\mathbb{F}}
\newcommand{\quadraticExtension}{\mathbb{E}}
\newcommand{\finiteFieldExtension}[1]{\finiteField_{#1}}
\newcommand{\quadraticFieldExtension}[1]{\quadraticExtension_{#1}}
\newcommand{\NormOneGroup}[1]{\finiteFieldExtension{#1}^{\aFieldNorm = 1}}
\newcommand{\algebraicClosure}[1]{\overline{#1}}
\newcommand{\Galois}{\operatorname{Gal}}
\newcommand{\Frobenius}{\operatorname{Fr}}
\newcommand{\restrictionOfScalars}[3]{\operatorname{Res}_{#1 \slash #2}{#3}}
\newcommand{\multiplcativeScheme}{\mathbb{G}_m}
\newcommand{\affineLine}{\mathbb{A}^1}
\newcommand{\squareMatrix}{\operatorname{Mat}}
\newcommand{\Mat}[2]{\operatorname{Mat}_{#1 \times #2}}
\newcommand{\GaussSum}[2]{\mathcal{G}\left(#1, #2\right)}
\newcommand{\dblJacobiSum}[2]{\mathcal{J}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\GaussSumScalar}[2]{\mathrm{G}\left(#1, #2\right)}
\newcommand{\dblJacobiSumScalar}[2]{\mathrm{J}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblVirtualJacobiSumScalar}[2]{\mathrm{j}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblGammaFactor}[3]{\Gamma^{\mathrm{dbl}}\left(#1 \times #2, #3\right)}
\newcommand{\dblGammaFactorSpace}[4]{\Gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\dblLanglandsGammaFactorSpace}[4]{\gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\GaussSumCharacter}[3]{\tau\left(#1 \times #2, #3\right)}
\newcommand{\ladicnumbers}{\algebraicClosure{\mathbb{Q}_{\ell}}}
\newcommand{\IsometryGroup}{\mathrm{Isom}}
\newcommand{\lieAlgebra}{\mathfrak{g}}
\newcommand{\DeligneLusztigInduction}[2]{\mathrm{R}_{#1}^{#2}}
\newcommand{\algebraicGroup}[1]{\boldsymbol{\mathrm{#1}}}
\newcommand{\LusztigSeries}[2]{\mathcal{E}\left(#1, (#2)\right)}
\newcommand{\characteristicPolynomial}{\operatorname{CharPoly}}
\newcommand{\DualFrobeniusFixedPoints}[2][\Frobenius^{\ast}]{\algebraicGroup{#2}^{\ast #1}}
\newcommand{\FrobeniusFixedPoints}[2][\Frobenius]{\algebraicGroup{#2}^{#1}}
\newcommand{\CharacterLattice}[1]{X^{\ast}\left(#1\right)}
\newcommand{\CocharacterLattice}[1]{X_{\ast}\left(#1\right)}

@@

\subsubsection{Geometric Conjugacy and Lusztig Series}
Let $\algebraicGroup{G}$ be a reductive group over $\finiteField$ and fix a maximal torus $\algebraicGroup{T}$ defined over $\finiteField$. The \emph{dual group over $\finiteField$} of $\algebraicGroup{G}$ with respect to the torus $\algebraicGroup{T}$ corresponds to the group $\algebraicGroup{G}^*$ with a dual torus $\algebraicGroup{T}^*$ and root datum
\[
    (\CharacterLattice{\algebraicGroup{T}^*},\Phi_{\algebraicGroup{T}^*},\CocharacterLattice{\algebraicGroup{T}^*},\Phi_{\algebraicGroup{T}^*}^\vee) \cong (\CocharacterLattice{\algebraicGroup{T}},\Phi_{\algebraicGroup{T}}^\vee,\CharacterLattice{\algebraicGroup{T}},\Phi_{\algebraicGroup{T}})
\]
such that the isomorphism respects the Frobenius actions on $\CharacterLattice{\cdot}$ and $\CocharacterLattice{\cdot}$.

>>>>

% Finite field macros
\newcommand{\FieldNorm}[2]{\mathrm{N}_{#1:#2}}
\newcommand{\aFieldNorm}{\mathrm{N}}
\newcommand{\finiteField}{\mathbb{F}}
\newcommand{\quadraticExtension}{\mathbb{E}}
\newcommand{\finiteFieldExtension}[1]{\finiteField_{#1}}
\newcommand{\quadraticFieldExtension}[1]{\quadraticExtension_{#1}}
\newcommand{\NormOneGroup}[1]{\finiteFieldExtension{#1}^{\aFieldNorm = 1}}
\newcommand{\algebraicClosure}[1]{\overline{#1}}
\newcommand{\Galois}{\operatorname{Gal}}
\newcommand{\Frobenius}{\operatorname{Fr}}
\newcommand{\restrictionOfScalars}[3]{\operatorname{Res}_{#1 \slash #2}{#3}}
\newcommand{\multiplcativeScheme}{\algebraicGroup{G}_m}
\newcommand{\affineLine}{\mathbb{A}^1}
\newcommand{\squareMatrix}{\operatorname{Mat}}
\newcommand{\Mat}[2]{\operatorname{Mat}_{#1 \times #2}}
\newcommand{\GaussSum}[2]{\mathcal{G}\left(#1, #2\right)}
\newcommand{\dblJacobiSum}[2]{\mathcal{J}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\GaussSumScalar}[2]{\mathrm{G}\left(#1, #2\right)}
\newcommand{\dblJacobiSumScalar}[2]{\mathrm{J}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblVirtualJacobiSumScalar}[2]{\mathrm{j}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblGammaFactor}[3]{\Gamma^{\mathrm{dbl}}\left(#1 \times #2, #3\right)}
\newcommand{\dblGammaFactorSpace}[4]{\Gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\dblLanglandsGammaFactorSpace}[4]{\gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\GaussSumCharacter}[3]{\tau\left(#1 \times #2, #3\right)}
\newcommand{\ladicnumbers}{\algebraicClosure{\mathbb{Q}_{\ell}}}
\newcommand{\IsometryGroup}{\mathrm{Isom}}
\newcommand{\lieAlgebra}{\mathfrak{g}}
\newcommand{\DeligneLusztigInduction}[2]{\mathrm{R}_{#1}^{#2}}
\newcommand{\algebraicGroup}[1]{\boldsymbol{\mathrm{#1}}}
\newcommand{\LusztigSeries}[2]{\mathcal{E}\left(#1, (#2)\right)}
\newcommand{\characteristicPolynomial}{\operatorname{CharPoly}}
\newcommand{\DualFrobeniusFixedPoints}[2][\Frobenius^{\ast}]{\algebraicGroup{#2}^{\ast #1}}
\newcommand{\FrobeniusFixedPoints}[2][\Frobenius]{\algebraicGroup{#2}^{#1}}
\newcommand{\CharacterLattice}[1]{X^{\ast}\left(#1\right)}
\newcommand{\CocharacterLattice}[1]{X_{\ast}\left(#1\right)}

@@

\subsubsection{Geometric Conjugacy and Lusztig Series}
Let $\ell$ be a prime number not equal to the characteristic of $\finiteField$. Fix an isomorphism $\ladicnumbers \cong \cComplex$.

Let $\algebraicGroup{G}$ be a reductive group over $\finiteField$ and fix a maximal $\Frobenius$-stable torus $\algebraicGroup{T} \subset \algebraicGroup{G}$ defined over $\finiteField$. We denote by $$\CharacterLattice{\algebraicGroup{T}} = \Hom_{\algebraicClosure{\finiteField}}\left(\algebraicGroup{T}, \multiplcativeScheme\right)$$ the \emph{character lattice} of $\algebraicGroup{T}$ and by $$\CocharacterLattice{\algebraicGroup{T}} = \Hom_{\algebraicClosure{\finiteField}}\left(\multiplcativeScheme, \algebraicGroup{T}\right)$$ the \emph{cocharacter lattice} of $\algebraicGroup{T}$, where we regard $\algebraicGroup{T}$ and $\multiplcativeScheme$ as algebraic groups over $\finiteField$. Recall that $\CharacterLattice{\algebraicGroup{T}}$ and $\CocharacterLattice{\algebraicGroup{T}}$ are free $\zIntegers$-modules of the same finite rank. The assignment $\CharacterLattice{\algebraicGroup{T}} \times \CocharacterLattice{\algebraicGroup{T}} \to \Hom_{\finiteField}\left(\multiplcativeScheme, \multiplcativeScheme\right)$ given by composition $\left(x,y\right) \mapsto \left(z \mapsto x\left(y\left(z\right)\right)\right)$ defines a pairing $\innerproduct{\cdot}{\cdot} \colon \CharacterLattice{\algebraicGroup{T}} \times \CocharacterLattice{\algebraicGroup{T}} \to \zIntegers$ by the rule $$x\left(y\left(z\right)\right) = z^{\innerproduct{x}{y}}.$$

The \emph{dual group over $\finiteField$} of $\algebraicGroup{G}$ with respect to the torus $\algebraicGroup{T}$ corresponds to the group $\algebraicGroup{G}^*$ with a dual torus $\algebraicGroup{T}^*$ and root datum
\[
(\CharacterLattice{\algebraicGroup{T}^*},\Phi_{\algebraicGroup{T}^*},\CocharacterLattice{\algebraicGroup{T}^*},\Phi_{\algebraicGroup{T}^*}^\vee) \cong (\CocharacterLattice{\algebraicGroup{T}},\Phi_{\algebraicGroup{T}}^\vee,\CharacterLattice{\algebraicGroup{T}},\Phi_{\algebraicGroup{T}})
\]
such that the isomorphism respects the Frobenius actions on $\CharacterLattice{\cdot}$ and $\CocharacterLattice{\cdot}$.
